`r params$doc_title`

### 2023-02-01 scripts/MSc.Rmd
updated purrr simulation, checked implementation speed

# for the numeric traits we have to map over sample size and recalculate se_updated
n.orig_sqrt <- sqrt(n.orig)
explained_variance_BMI2_sample_size <- map(n, ~explained_variance_numeric2(maf = my_data_harm$eaf.bmi, beta = my_data_harm$beta.bmi, 
                                                                           se_beta = abs(my_data_harm$beta.bmi / -qnorm(p=(my_data_harm$p.value.bmi / 2), mean = 0) * n.orig_sqrt / sqrt(.x)), 
                                                                           samplesize = .x))

cum_expl_varX2_sample_size <- c()
for (mysamples in 1:length(colnames_pval)) {
  temp_dat <- my_data_harm %>% 
    select(all_of(colnames_pval[mysamples])) %>% 
    mutate(explained_variance_BMI2_sample_size = explained_variance_BMI2_sample_size[[mysamples]]) %>% 
    filter(!!sym(colnames_pval[mysamples]) < threshold)
  #print(temp_dat)
  cum_expl_varX2_sample_size <- append(cum_expl_varX2_sample_size, sum(temp_dat$explained_variance_BMI2_sample_size))
}

>>>>

# for the numeric traits we have to map over sample size and recalculate se_updated
explained_variance_BMI2_sample_size <- map(n, ~explained_variance_numeric2(maf = my_data_harm$eaf.bmi, beta = my_data_harm$beta.bmi, 
                                                                           se_beta = abs(my_data_harm$beta.bmi / -qnorm(p=(my_data_harm$p.value.bmi / 2), mean = 0) * sqrt(n.orig) / sqrt(.x)), 
                                                                           samplesize = .x))

cum_expl_varX2_sample_size <- c()
for (mysamples in 1:length(colnames_pval)) {
  temp_dat <- my_data_harm %>% 
    select(all_of(colnames_pval[mysamples])) %>% 
    filter(!!sym(colnames_pval[mysamples]) < threshold) %>% 
    mutate(explained_variance_BMI2_sample_size = explained_variance_BMI2_sample_size[[mysamples]])
  #print(temp_dat)
  cum_expl_varX2_sample_size <- append(cum_expl_varX2_sample_size, sum(temp_dat$explained_variance_BMI2_sample_size))
}
